Disparities in Climate-Induced Health Outcomes in the Greater Toronto Area.

### 2022-06-22 outputs/paper/paper.qmd
Update paper.qmd
Updating paper.qmd

## Visualizing the Data and the Implications

#### Visualizing Temperature from 2002-2022

@@

ggplot(dec_mar, aes(x=year, y=max_temp, color=month_name)) + geom_point()

@@

ggplot(apr_jul, aes(x=year, y=max_temp, color=month_name)) + geom_point()

@@

ggplot(aug_nov, aes(x=year, y=max_temp, color=month_name)) + geom_point()

@@

#### Implications 1

#### Visual 2

#### Implications 2

#### Visuals 3

#### Implications 3

>>>>

## Visualizing Temperature from 2002-2022

#### Visualizing Temperature by Months

@@

ggplot(dec_mar, aes(x=year, y=max_temp, color=month_name)) + geom_point() + 
  labs(color="Month") + xlab("Year") + ylab("Maximum Temperature")

@@

ggplot(apr_jul, aes(x=year, y=max_temp, color=month_name)) + geom_point() + 
  labs(color="Month") + xlab("Year") + ylab("Maximum Temperature")

@@

ggplot(aug_nov, aes(x=year, y=max_temp, color=month_name)) + geom_point() + 
  labs(color="Month") + xlab("Year") + ylab("Maximum Temperature")

@@
